The \dealii{} Library, Version 9.0

### 2018-04-19 9.0/paper.tex
Update Acknowledgments
 - break overlong lines

 - The DFG calls itself "German Research Foundation" on their English
   website. Update naming

 - Try to unify naming

 - add my own funding

% W.~Bangerth was partially
% supported by the National Science Foundation under award OCI-1148116
% as part of the Software Infrastructure for Sustained Innovation (SI2)
% program; and by the Computational Infrastructure in Geodynamics initiative
% (CIG), through the National Science Foundation under Awards
% No.~EAR-0949446 and EAR-1550901 and The University of California -- Davis.
%
V.~Boddu was supported by the German Science Foundation (Deutsche 
Forschungs-Gemeinschaft, DFG) under the research group project FOR 1509.

@@

D.~Davydov was supported by the German Science Foundation
(Deutsche Forschungs-Gemeinschaft, DFG), grant DA 1664/2-1.

T.~Heister was partially supported by the Computational Infrastructure in
Geodynamics initiative (CIG), through the National Science Foundation
under Award No. EAR-0949446 and EAR-1550901 and The University of California -- Davis, and National Science Foundation grant DMS-1522191.

@@

>>>>

% W.~Bangerth was partially
% supported by the National Science Foundation under award OCI-1148116
% as part of the Software Infrastructure for Sustained Innovation (SI2)
% program; and by the Computational Infrastructure in Geodynamics initiative
% (CIG), through the National Science Foundation under Awards
% No.~EAR-0949446 and EAR-1550901 and The University of California -- Davis.

V.~Boddu was supported by the German Research Foundation (DFG) under the
research group project FOR 1509.

@@

D.~Davydov was supported by the German Research Foundation (DFG), grant DA
1664/2-1.

T.~Heister was partially supported by the Computational Infrastructure in
Geodynamics initiative (CIG), through the National Science Foundation (NSF)
under Award No. EAR-0949446 and EAR-1550901 and The University of
California -- Davis, and NSF Grant DMS-1522191.

@@

M.~Maier was partially supported by ARO MURI Award No. W911NF-14-0247.
